Quick, Draw! Image Classification

### 2018-12-07 report/draft.tex
see draft updates

We generate hypotheses based on expectations related to model performance. We
then conduct preprocessing steps on our data.

@@

\begin{align*}
  H1_a: &\text{Fully Connected Neural Network will struggle} \\
  &\text{ to get reasonable accuracy.} \\
  H2_a: &\text{CNN should perform better than fully} \\
  &\text{connected neural network.} \\
\end{align*}

\subsubsection{Addressing data component of performance}
\begin{align*}
  H3_a: &\text{Small amounts of data will lead to overfitting.} \\
  H4_a: &\text{Imbalanced class prediction can be improved}\\
  &\text{using data augmentation.} \\
  H5_a: &\text{Addition of a category to the trained model will} \\
  &\text{reduce the performance of the model.} \\
  H6_a: &\text{Adding more training data will improve the} \\
  &\text{performance of the model.} \\
\end{align*}

@@

Loss Function: Categorical Cross Entropy [TO DO: Why?]
Optimizer: [TODO: Why?]
Number of Trainable Parameters: 320,890

The number of clearly being much greater than the number of observations used
to train the model, we need to reduce the number of parameters vis-a-vis
number of observations. From the available strategies to do so, we
incorporated MaxPooling [TO DO: why?] post each convolution operation, in
order to extract only the most significant features. As as a consequence,
this reduced the volume of the output, giving the model a smaller memory
footprint as well as a smaller number of trainable parameters.

>>>>

Our methodology consists of reviewing statistical methodology, presenting
theoretically informed hypotheses, and providing an overview of our data.

@@

\begin{itemize}
  \item[$H1_a$] Fully Connected Neural Network will struggle to get reasonable
    accuracy.
  \item[$H2_a$] CNN should perform better than fully connected neural network.
  \end{itemize}

\subsubsection{Addressing data component of performance}

\begin{itemize}
\item[$H3_a$] Small amounts of data will lead to overfitting.
\item[$H4_a$] Imbalanced class prediction can be improved using data
  augmentation.
\item[$H5_a$] Addition of a category to the trained model will reduce the
  performance of the model.
\item[$H6_a$] Adding more training data will improve the performance of the
  model.
\end{itemize}

@@

\subsubsection{Understanding the Loss Function}

Most modern neural networks are trained using maximum likelihood. This
means that the cost function is the negative log-likelihood, also
described as the cross-entropy between the training data and the model
distribution \cite{Goodfellow-et-al-2016}. In our use case, we are interested
in correctly classifying 10 categories of drawings. Our output unit
use a Softmax function in our output layer because they are most often
used for classifiers representing the probability distribution over
$n$ different classes. Given features $h$, weights $W$, and bias $b$, a
linear layer first predicts unnormalized log probabilities:
\begin{equation}
  z = W^Th + b 
\end{equation}

where $z_i = \log \tilde{P}(y = i | x)$. The softmax function can then
exponentiate and normalize $z$ to obtain the desired $\hat{y}$. The
softmax function is given by
\begin{equation}
  \func{softmax}(z)_i = \frac{\exp(z_i)}{\sum_j \exp(z_j)}.
\end{equation}

As a cost function, we wish to maximize
$\log P(y=i; z) = \log \func{softmax}(z)_i$. We can do this formally as
\begin{equation}
  \log \func{softmax}(z)_i = z_i - \log \sum_j \exp(z_j).
\end{equation}

which gives us the intuition for a single example. Overall, we want to learn
parameters that drive the softmax to predict the fraction of counts of each
outcome observed in the training set \cite{Goodfellow-et-al-2016}:
\begin{equation}
  \func{softmax}(z(x;\theta))_i \approx \frac{\sum_{j=1}^m 1_{y^{(j)} = i,
      x^{(j)} = x}}{\sum_{j=1}^m 1_{x^{(j)} = x}}.
\end{equation}

This is how the $\func{categorical\_crossetropy}(\text{y\_true}, \text{y\_pred})$ function is constructed in Keras \cite{chollet2015keras} as well as the
$\func{softmax\_cross\_entropy\_with\_logits\_v2}(\text{labels}, \text{logits})$
in Tensorflow \cite{tensorflow2015-whitepaper}.

\subsubsection{Understanding the Optimization Technique}

There are a number of different optimization methods such as Stochastic
and Batch Gradient descent. In practice, we chose to use a faster variant
of gradient descent called Adam. The Adam optimization is able to use
an exponentially weighted average of the gradients, a technique called
momentum, and then use that gradient to update your weights instead. We
also want to slow down gradient descent in the horizontal direction, a
technique called RMSprop), to reduce oscillations from batch gradient descent.
The Adam optimization method is combining momentum and RMSprop to perform
gradient descent more quickly \cite{DeepLear51:online}.

Number of Trainable Parameters: 320,890

The number of clearly being much greater than the number of observations used
to train the model, we need to reduce the number of parameters vis-a-vis
number of observations. From the available strategies to do so, we
incorporated MaxPooling [TODO: why?] post each convolution operation, in
order to extract only the most significant features. As as a consequence,
this reduced the volume of the output, giving the model a smaller memory
footprint as well as a smaller number of trainable parameters.
